---
title: "A Minimal Example"
author: "RS"
date: "March 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

We examine the relationship between speed and stopping distance using a linear regression model: $Y = \beta_0 + \beta-1 x + \epsilon$.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

## Use cars data set (provided)

```{r cars}
summary(cars)
```

## Plot dist vs speed

Embed a plot thus: 

```{r regression model, fig.width=4, fig.height=3, fig.aligh='center', echo=FALSE}
par(mar = c(4,4,1,1), mgp = c(2,1,0), cex= 0.8)
plot(cars, pch=20, col='darkgray')
fit <- lm(dist ~ speed, data = cars)
abline(fit, lwd =2)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

The slope of a simple linear regression is
`r coef(fit)[2]`
